Stack Safety as a Security Property

### 2020-07-07 main.tex
Fixed confidentiality example

\definition{Trace Confidentiality} We will say two traces $MP$ and $M$
satisfy {\em trace confidentiality} with respect to $\contour$ if:
\begin{itemize}
\item If $\MPT$ is finite and its final state $\mach_r$ is a valid
  return\leo{Is this ill-scoped?}, then $\machT$ is also finite with some final state $\mach_r'$ and
  any changes from the initial states have changed in the same way:
$$\forall \component. ~ \mach_e(\component) \not = \mach_r(\component)
  \vee \mach_e'(\component) \not = \mach_r'(\component) \rightarrow
  \mach_r(\component) = \mach_r'(\component)$$
  In addittion their observations must be equivalent:
  $$\pi_o(\MPT) \eqsim \pi_o(\machT)$$
\item If $\MPT$ is infinite, then $\machT$ is also infinite and their
  observations are equivalent:
  $$\pi_o(\MPT) \eqsim \pi_o(\machT)$$
\item If the $\MPT$ ends prematurely with a policy fault, then
  we require that its observations are a prefix of those of $\machT$:
  $$\pi_o(\MPT) \lesssim \pi_o(\machT)$$
\end{itemize}

@@

      In our example, \cref{fig:conflex} shows how execution continues from
      \(\mach_r'\) and the restored \(\mach_r'' = \mathit{restore}(\contour,
      \mach_e,\mach_e',\mach_r,\mach_r')\). Addresses 108 and 109, in pink, are
      not restored; every address that was varied and not changed in one of the
      executions is. Since 108 contains a value that originates in the
      variation, values that depend on it might be anything; after returning
      from {\tt g}, {\tt main} prints 95 in the trace from \(\mach_r\) and
      some undetermined value in the trace from \(\mach_r''\). So observable
      trace confidentiality does not hold.
      \rb{Color name macro}

>>>>

\definition{Trace Confidentiality} We will say two traces $MP$ and $M$
satisfy {\em trace confidentiality} with respect to $\contour$ and
a return predicate \(R \subset \MACHS\) if:
\begin{itemize}
\item If $\MPT$ is finite and its final state $R\ \mach_r$,
  then $\machT$ is also finite with some final state $\mach_r'$ and
  any changes from the initial states have changed in the same way:
$$\forall \component. ~ \mach_e(\component) \not = \mach_r(\component)
  \vee \mach_e'(\component) \not = \mach_r'(\component) \rightarrow
  \mach_r(\component) = \mach_r'(\component)$$
  In addition their observations must be equivalent:
  $$\pi_o(\MPT) \eqsim \pi_o(\machT)$$
\item If $\MPT$ is infinite, then $\machT$ is also infinite and their
  observations are equivalent:
  $$\pi_o(\MPT) \eqsim \pi_o(\machT)$$
\item If the $\MPT$ ends prematurely, without fulfilling \(R\), then
  we require that its observations are a prefix of those of $\machT$:
  $$\pi_o(\MPT) \lesssim \pi_o(\machT)$$
\end{itemize}

@@

      In our example, \cref{fig:conflex} shows how execution continues from
      \(\mach_r'\) and the restored \(\mach_r'' = \mathit{restore}(\contour,
      \mach_e,\mach_e',\mach_r,\mach_r')\). Addresses 108 and 109, in \tainted,
      are not restored; every address that was varied and not changed in one
      of the executions is. Since 108 contains a value that originates in the
      variation, values that depend on it might be anything; after returning
      from {\tt g}, {\tt main} prints 95 in the trace from \(\mach_r\) and
      some undetermined value in the trace from \(\mach_r''\). So observable
      trace confidentiality does not hold.
      \rb{Color name macro}
